---
title: "iq_reclass"
author: "Luke Salvato"
date: "11/24/2020"
output: 
  html_document:
  toc_float: true
  theme: default
  highlight: tango
  
---
####Packages
```{r packages}
library(sf)
library(raster)
library(tmap) 
library(tmaptools)
library(tidyverse)
```

#DATA
```{r data}
getwd()

land_iq_reclass <- jsonlite::fromJSON("/Users/lukesalvato/Dropbox/Mac (3)/Documents/Land_Use/rice_area/data/raw/full_iq_reclass_20220302.geojson")
```



```{r}
df_tib<- tibble(year_code=c(
"CDL_2007b",
"CDL_2008",
"CDL_2009",
"CDL_2010",
"CDL_2011",
"CDL_2012",
"CDL_2013",
"CDL_2014",
"CDL_2015",
"CDL_2016",
"CDL_2017",
"CDL_2018",
"CDL_2019",
"CDL_2020",
"CDL_2021")) %>% 
  mutate("year" = cbind(2007:2021))
```

```{r}
data_extract <- df_tib%>%
  mutate(data = map(year_code, ~pull(land_iq_reclass$features$properties,.)%>%
                        mutate(OBJECTID_1=land_iq_reclass$features$properties$OBJECTID_1)%>%
                      mutate(Crop2016 = land_iq_reclass$features$properties$Crop2016)%>% 
                      pivot_longer(c(-OBJECTID_1, -Crop2016),
                                   values_to="count", names_to="CDL_class") %>%
                      filter(!is.na(count)))) %>% 
      unnest(data)%>%
  dplyr::select(-year_code) %>%
  group_by(OBJECTID_1, year) %>%
  mutate(pixel_sum = sum(count),
         count_perc = 100* count/pixel_sum) %>%
  ungroup() %>%
  dplyr::select(OBJECTID_1, everything())
```

```{r}
data_mode <- data_extract %>%
  group_by(OBJECTID_1, year) %>%
  filter(count_perc==max(count_perc)) %>%
  ungroup()

data_mode %>%
  ggplot(aes(x=count_perc))+
  geom_histogram()
```

```{r}
data_mode_then_has_rice <- data_extract %>%
  group_by(OBJECTID_1, year) %>%
  filter(count_perc==max(count_perc)) %>%
  ungroup() %>% 
  mutate(rice = case_when(CDL_class == "3" ~ 1,
                          CDL_class != "3" ~ 0)) %>% 
  group_by(OBJECTID_1) %>% 
  mutate(has_rice = sum(rice)) %>% 
  ungroup()%>% 
  filter(has_rice > 0)




data_mode_then_has_rice %>% 
  ggplot(aes(x=count_perc))+
  geom_histogram(binwidth = 1)
```


```{r}
data_select <- data_mode_then_has_rice %>%
  group_by(OBJECTID_1) %>% 
  mutate(m2 = round(pixel_sum*900, 2)) %>% 
  mutate(acres = round(m2*0.000247105, 2)) %>% 
  ungroup() %>% 
  mutate(year=as.numeric(year))



#summar <- data_select %>% group_by(CDL_class) %>% summarise(acreage = sum(acres)) #%>% 
  

#categories <- unique(data_select$CDL_class) 
#numberOfCategories <- length(categories)

crops <- data_select  %>% 
  mutate(Crop = case_when(CDL_class==3~"rice",
                          CDL_class==61~"fallow",
                          CDL_class==36~"alfalfa",
                          CDL_class==76~"walnut",
                          CDL_class==75~"almond",
                          CDL_class %in% c(176,37)~"grasses", #grassland/ pasture
                          CDL_class %in% c(24,42,1,33,54,6)~"annual crop", 
                          #winter wheat, dry beans, corn, safflower, tomatoes, sunflower
                          CDL_class %in% c(195,111,121,131,190,63,44,122,123,124,92,152)~"other other", 
                          #herbaceous wetland, open water, developed/open space, barren, woody wetlands, forest, other crops, developed/low intensity, developed/med intesnity, aquaculture, shrubland
                          CDL_class %in% c(27,224,205,4,28,59,2,213,53,22,49,13,50,236,58,48,226,225,222,
                                           221,216,207,21,209,229,234,29,244,43,31, 47,208,23,51,12,228)~"other annual", 
                          #rye, vetch, triticale, sorghum, oats, sod/grass seed, cotton, honeydew melons, peas, durum wheat, onions, pop or orn corn, cucumbers, dbl crop wint wheat/sorgum, double crop oats, corn, squash, strawberries, peppers, asparagus, barley, cantaloupes, pumpkins, dbl crop durum wht/sorgum, millet, cauliflower, potatoes, canola, misc fuits & vegetables, garlic, spring wheat, chick peas, sweet corn, double crop triticale/corn. 
                          TRUE ~ "other perennial")) %>% 
  dplyr::select(-CDL_class) %>% 
  mutate(crop_year = as.character(paste0("crop_", year, "_name"))) %>% 
  unnest(crop_year)

summar <- crops %>% group_by(Crop, year) %>% summarise(acreage = sum(acres))
getwd()
write_csv(crops, "/Users/lukesalvato/Dropbox/Mac (3)/Documents/Land_Use/soils/data/07_to_21_CDL_reclassifed_20220726.csv")
```


```{r}
crops_wide <- crops %>% 
  dplyr::select(OBJECTID_1, crop_year, Crop, acres) %>% 
  pivot_wider(names_from = crop_year, values_from = Crop, values_fn = list) %>% 
  group_by(OBJECTID_1, acres) %>% 
  ungroup %>% 
  unnest(cols = c(crop_2007_name, crop_2008_name, crop_2009_name, crop_2010_name, 
    crop_2011_name, crop_2012_name, crop_2013_name, crop_2014_name, 
    crop_2015_name, crop_2016_name, crop_2017_name, crop_2018_name, 
    crop_2019_name, crop_2020_name, crop_2021_name))
  #unite(string, "2008":"2019", sep = "", remove = TRUE, na.rm = TRUE) %>% 
  #mutate(rotations = str_count(string, "10"))
getwd()
#write_csv(crops_wide, "/Users/lukesalvato/Dropbox/Mac (3)/Documents/Land_Use/soils/data/07_to_21_CDL_reclassifed_WIDE_20220726.csv")
```


```{r}
diff <- crops_wide %>% 
  mutate("2008" = paste0(crop_2007_name,
                            " -> ", 
                            crop_2008_name)) %>%
  mutate("2009" = paste0(crop_2008_name,
                            " -> ", 
                            crop_2009_name)) %>%
  mutate("2010" = paste0(crop_2009_name,
                            " -> ", 
                            crop_2010_name)) %>%
  mutate("2011" = paste0(crop_2010_name,
                            " -> ", 
                            crop_2011_name)) %>%
  mutate("2012" = paste0(crop_2011_name,
                            " -> ", 
                            crop_2012_name)) %>%
  mutate("2013" = paste0(crop_2012_name,
                            " -> ", 
                            crop_2013_name)) %>%
  mutate("2014" = paste0(crop_2013_name,
                            " -> ", 
                            crop_2014_name)) %>%
  mutate("2015" = paste0(crop_2014_name,
                            " -> ", 
                            crop_2015_name)) %>%
  mutate("2016" = paste0(crop_2015_name,
                            " -> ", 
                            crop_2016_name)) %>%
  mutate("2017" = paste0(crop_2016_name,
                            " -> ", 
                            crop_2017_name)) %>%
  mutate("2018" = paste0(crop_2017_name,
                            " -> ", 
                            crop_2018_name)) %>%
  mutate("2019" = paste0(crop_2018_name,
                            " -> ", 
                            crop_2019_name)) %>% 
    mutate("2020" = paste0(crop_2019_name,
                            " -> ", 
                            crop_2020_name)) %>% 
    mutate("2021" = paste0(crop_2020_name,
                            " -> ", 
                            crop_2021_name)) %>% 
  dplyr::select(OBJECTID_1, acres, as.character(2008:2021))
  
  #dplyr::select(OBJECTID_1, acres, "2008", "2009","2010", "2011","2012", "2013","2014","2015","2016","2017","2018","2019")

getwd()
#save to SSURGO
#write_csv(diff, "/Users/lukesalvato/Dropbox/Mac (3)/Documents/Land_Use/soils/data/07_to_21_change_detection_20220726.csv")

```

```{r}
diff <- read_csv("/Users/lukesalvato/Dropbox/Mac (3)/Documents/Land_Use/soils/data/07_to_21_change_detection_20220726.csv")

diff_long <- diff %>% 
  pivot_longer(cols = 3:16, names_to = "year", values_to = "type")
```

JOIN TO GEOMETRIES
```{r}
fields <- st_read("/Users/lukesalvato/Dropbox/Mac (3)/Documents/Land_Use/soils/data/all_fields_no_wetland_no_urban") %>% 
  dplyr::select(OBJECTID_1) %>%
  st_zm() 


crops_field_join <- left_join(crops_wide, fields, by = "OBJECTID_1")
getwd()
st_write(crops_field_join, "/Users/lukesalvato/Dropbox/Mac (3)/Documents/Land_Use/rice_area/reclassified_CDL/data/2007_to_2021_rice_area_fields_and_crops_20220413.geojson", delete_layer = TRUE)
#2007_to_2021_rice_area_fields_and_crops_20220302.geojson


diff_field_join <- left_join(diff, fields, by="OBJECTID_1")
getwd()
#st_write(diff_field_join, "2007_to_2018_cdl_reclassified_with_iq.shp")
```

GET COUNTIES
```{r}
counties <- st_read("/Users/lukesalvato/Dropbox/Mac (3)/Documents/Land_Use/rice_area/data/raw/CA_Counties") %>% 
  dplyr::select(NAME) %>%
  st_zm() %>% 
  filter(NAME %in% c("Sutter", "Butte", "Glenn", "Colusa", "Yolo", "Sacramento", "Placer", "San Joaquin", "Yuba", "Tehama", "Nevada", "Merced", "Stanislaus","Solano", "Contra Costa", "Alameda", "Fresno", "Madera")) %>% 
  st_as_sf()
```

# Fields and Counties spatial Join
Make county level acreage estimates
```{r}
crops_fields_sf <- crops_field_join %>% 
  st_as_sf()

crops_fields_sf %>% 
  pivot_longer(c(-OBJECTID_1, -acres, -geometry),
                                 values_to="type", names_to="year") %>% 
  filter(type  == "rice") %>% 
  group_by(year) %>% 
  summarise(acreage = sum(acres))



counties_sf <- counties %>% 
  st_as_sf() %>% 
    st_transform(crs = st_crs(crops_fields_sf))

counties_fields_join <- st_join(counties_sf, crops_fields_sf)

cfj_long <- counties_fields_join %>% 
    pivot_longer(c(-OBJECTID_1, -acres, -geometry, -NAME),
                                 values_to="type", names_to="year")

county_level_acreage <- cfj_long %>% 
  filter(type  == "rice") %>% 
  group_by(NAME, year) %>% 
  summarise(acreage = sum(acres))

write_csv(county_level_acreage, file = "/Users/lukesalvato/Dropbox/Mac (3)/Documents/Land_Use/NASS/data/processed/CDL_reclassified_county_level_acreage_20221024.csv")
```

557031.4			
506358.8			
540083.2			
539627.8			
561340.2			
542331.2			
549933.9			
445247.2			
424115.8			
527064.5	
433788.7			
494702.6			
489479.1			
504237.7			
396783.3	

FROM RICE TO PERENNIAL DIFF PLOT
```{r}
s <- diff_long %>%
  complete(year,type, fill = list(acres=2)) %>% 
  filter(type %in% c("rice -> almond", "rice -> walnut", "rice -> other perennial")) %>% 
  group_by(year, type) %>%
  summarise(acreage = sum(acres))
 
ggplot(data=s, aes(x=year, y=acreage, fill=type)) +
geom_bar(stat="identity", position=position_dodge(), color = "black")+
  scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9"))+
  scale_y_continuous(name = "Acres", labels = scales::comma) +
  xlab("Change From Previous Year")+
  theme_minimal() +
   theme(legend.position = c(0.8, 0.8))+
  theme(axis.text=element_text(size=12))+
  theme(legend.background = element_rect(size=0.5, linetype="solid"))+
  theme(legend.title = element_blank())+
  ggtitle("Change from Rice to Perennial")
 

```

PERENIIAL DIFF MAP
```{r}
library(tmap)

p1 <- diff_field_join %>% 
  as_tibble() %>% 
  pivot_longer(c(-OBJECTID_1, -acres, -geometry),
                                 values_to="type", names_to="year") %>% 
  filter(type %in% c("rice -> almond", "rice -> walnut", "rice -> other perennial")) %>%
  rename("field size (acres)" = acres) %>% 
  st_sf() %>% 
  st_centroid()

tmap_mode("plot")
perennial <- tm_basemap("OpenStreetMap.Mapnik") +
  tm_shape(p1) +
  tm_dots(shape = "type", col = "year", size = "field size (acres)")+
  #tm_shape(counties)+
  #tm_polygons(alpha = 0)+
  #tm_text("NAME", size = 0.7, alpha = 0.5)+
   tm_layout(legend.outside = TRUE)
perennial
getwd()
tmap_save(perennial, filename="perennial_map.png")
```

TO ALMOND (FROM ALL) PLOT
```{r}
to_almond <- diff_long %>%
  complete(year,type, fill = list(acres=2)) %>% 
  #filter(type %in% c("rice -> almond", "rice -> walnut", "rice -> other perennial")) %>% 
  filter(str_detect(type, pattern = "-> almond")) %>% 
  filter(!type %in% c("almond -> almond" , "walnut -> almond",
                      "other other -> almond")) %>% 
  group_by(year, type) %>%
  summarise(acreage = sum(acres)) %>% 
  ungroup() %>% 
  #group_by(year) %>% 
  mutate(type = fct_reorder(type, desc(-acreage))) %>% 
  ungroup()
 
ggplot(data=to_almond, aes(x=year, y=acreage, fill=type)) +
geom_bar(stat="identity", #position=position_dodge(), 
         color = "black")+
  scale_fill_manual(values=c(#"#000000","#999999","#FFDB6D", 
                             "#C4961A", "#F4EDCA", 
                "#D16103", "#C3D7A4", "#52854C", "#4E84C4", "#293352"))+
  scale_y_continuous(name = "Acres", labels = scales::comma) +
  xlab("Change From Previous Year")+
  theme_minimal() +
   theme(legend.position = c(0.3, 0.7))+
  theme(axis.text=element_text(size=12))+
  theme(legend.background = element_rect(size=0.5, linetype="solid"))+
  theme(legend.title = element_blank())+
  ggtitle("Change to Almond")
 

```
TO ALMOND MAP
```{r}
to_a <- diff_field_join %>% 
  as_tibble() %>% 
  pivot_longer(c(-OBJECTID_1, -acres, -geometry),
                                 values_to="type", names_to="year") %>% 
  #filter(type %in% c("rice -> almond", "rice -> walnut", "rice -> other perennial")) %>%
  filter(str_detect(type, pattern = "-> almond")) %>% 
  filter(!type %in% c("almond -> almond" , "walnut -> almond",
                      "other other -> almond")) %>% 
  rename("field size (acres)" = acres) %>% 
  st_sf() %>% 
  st_centroid()

tmap_mode("plot")
new_alm <- tm_basemap("OpenStreetMap.Mapnik") +
  tm_shape(to_a) +
  tm_dots(col = "year", size = 0.4, alpha = 0.9, palette = "viridis", legend.hist = TRUE)+#, col = "year")+#, size = "field size (acres)")+
#  tm_shape(counties)+
#  tm_polygons(alpha = 0)+
 # tm_text("NAME", size = 0.7, alpha = 0.5)+
   tm_layout(legend.outside = TRUE, legend.text.size = 2 , title = "New Almond Fields")
new_alm
getwd()
tmap_save(new_alm, filename="new_alm_map.png")
```
TOTAL ALMOND / WALNUT ACREAGE PLOT
```{r}

crops1 <- crops %>% 
  mutate(year = as_factor(year)) %>% 
  group_by(Crop) %>% 
  mutate(Crop = fct_reorder(Crop, desc(acres))) %>% 
  ungroup() %>% 
  mutate(year = paste0("'",str_sub(year, start=3))) 
  
#unique(crops1$Crop) 
#length(categories)

crops1 %>% 
  mutate(Crop = factor(Crop, levels = c("walnut", "almond","alfalfa", "other annual", "grasses", "other perennial", "other other", "annual crop","fallow","rice"))) %>% 
  filter(Crop == "almond") %>% 
ggplot(aes(x=year, y=acres, fill=Crop, group = Crop)) +
geom_bar(stat="identity")+#, color = "black")+
  scale_fill_manual(values=c("#000000","#999999","#FFDB6D", "#C4961A", "#F4EDCA", 
                "#D16103", "#C3D7A4", "#52854C", "#4E84C4", "#293352"))+
  scale_y_continuous(name = "Acres", labels = scales::comma) +
  xlab("")+
  theme_minimal() +
   #theme(legend.position = c(1.2, 1.2))+
  theme(axis.text=element_text(size=12))+
  theme(legend.background = element_rect(size=0.5, linetype="solid"))+
  theme(legend.title = element_blank())+
  ggtitle("Almond Acreage") 
  #geom_hline(yintercept=c(100000,200000,300000,400000,500000,600000), size = .5)


crops1 %>% 
  mutate(Crop = factor(Crop, levels = c("walnut", "almond","alfalfa", "other annual", "grasses", "other perennial", "other other", "annual crop","fallow","rice"))) %>% 
  filter(Crop == "walnut") %>% 
ggplot(aes(x=year, y=acres, fill=Crop, group = Crop)) +
geom_bar(stat="identity")+#, color = "black")+
  scale_fill_manual(values=c("#000000","#999999","#FFDB6D", "#C4961A", "#F4EDCA", 
                "#D16103", "#C3D7A4", "#52854C", "#4E84C4", "#293352"))+
  scale_y_continuous(name = "Acres", labels = scales::comma) +
  xlab("")+
  theme_minimal() +
   #theme(legend.position = c(1.2, 1.2))+
  theme(axis.text=element_text(size=12))+
  theme(legend.background = element_rect(size=0.5, linetype="solid"))+
  theme(legend.title = element_blank())+
  ggtitle("Walnut Acreage") 

```


TO WALNUT (FROM ALL) PLOT
```{r}
to_walnut <- diff_long %>%
  complete(year,type, fill = list(acres=2)) %>% 
  #filter(type %in% c("rice -> almond", "rice -> walnut", "rice -> other perennial")) %>% 
  filter(str_detect(type, pattern = "-> walnut")) %>% 
  filter(!type %in% c("almond -> walnut" ,
                      "walnut -> walnut",
                      "other other -> walnut"
                      )) %>% 
  group_by(year, type) %>%
  summarise(acreage = sum(acres)) %>% 
  ungroup() %>% 
  #pivot_wider(names_from = type, values_from = acreage, values_fn = list) %>%
  #select(-year) %>% 
  #transmute(total=rowSums(.))
  mutate(type = fct_reorder(type, desc(-acreage))) %>% 
  ungroup()
 
ggplot(data=to_walnut, aes(x=year, y=acreage, fill=type)) +
geom_bar(stat="identity", #position=position_dodge(),
         color = "black")+
  scale_fill_manual(values=c("#000000","#999999","#FFDB6D", 
                             "#C4961A", "#F4EDCA", 
                "#D16103", "#C3D7A4", "#52854C", "#4E84C4", "#293352"))+
  scale_y_continuous(name = "Acres", labels = scales::comma) +
  xlab("Change From Previous Year")+
  theme_minimal() +
   theme(legend.position = c(0.3, 0.7))+
  theme(axis.text=element_text(size=12))+
  theme(legend.background = element_rect(size=0.5, linetype="solid"))+
  theme(legend.title = element_blank())+
  ggtitle("Change to Walnut")
 

```
```{r}
m <- mtcars %>% select(cols) #%>% transmute(x=rowSums(.))
```



TO WALNUT MAP
```{r}
to_w <- diff_field_join %>% 
  as_tibble() %>% 
  pivot_longer(c(-OBJECTID_1, -acres, -geometry),
                                 values_to="type", names_to="year") %>% 
  #filter(type %in% c("rice -> almond", "rice -> walnut", "rice -> other perennial")) %>%
   filter(str_detect(type, pattern = "-> walnut")) %>% 
  filter(!type %in% c("almond -> walnut" ,
                      "walnut -> walnut",
                      "other other -> walnut")) %>% 
  rename("field size (acres)" = acres) %>% 
  st_sf() %>% 
  st_centroid()

tmap_mode("plot")
new_wal <- tm_basemap("OpenStreetMap.Mapnik") +
  tm_shape(to_w) +
  tm_dots(col = "year", size = 0.4, alpha = 0.9, palette = "viridis", legend.hist = TRUE )+#, col = "year")+#, size = "field size (acres)")+
 # tm_shape(counties)+
#  tm_polygons(alpha = 0)+
 # tm_text("NAME", size = 0.7, alpha = 0.5)+
   tm_layout(legend.outside = TRUE, legend.text.size = 1.5 , title = "New Walnut Fields")
new_wal
getwd()
tmap_save(new_wal, filename="new_wal_map.png")


```

PERENNIAL FAILURES PLOT
```{r}
per_fail_fig <- diff_long %>%
  complete(year,type, fill = list(acres=2)) %>% 
  #filter(type %in% c("rice -> almond", "rice -> walnut", "rice -> other perennial")) %>% 
  filter(str_detect(type, pattern = c("walnut ->", "almond ->"))) %>% 
   filter(type %in% c("almond -> rice", "walnut -> rice",
                     "almond -> annual crop", "walnut -> annual crop",
                     #"almond -> alfalfa", "walnut -> alfalfa", 
                     "almond -> fallow", "walnut -> fallow")) %>% 
  # #filter(!type %in% c("almond -> walnut" ,
  #                     "walnut -> walnut",
  #                     "walnut -> almond",
  #                     "almond -> almond",
  #                     "walnut -> other perennial",
  #                     "almond -> other perennial")) %>% 
  group_by(year, type) %>%
  summarise(acreage = sum(acres)) %>% 
  ungroup() %>% 
  #pivot_wider(names_from = type, values_from = acreage, values_fn = list) %>%
  #select(-year) %>% 
  #transmute(total=rowSums(.))
  #mutate(type = fct_reorder(type, desc(-acreage))) %>% 
  ungroup()

per_fail_fig %>% 
  mutate(type = factor(type, levels = c("almond -> annual crop", "almond -> fallow","almond -> rice", "walnut -> annual crop", "walnut -> fallow", "walnut -> rice"))) %>%
ggplot(aes(x=year, y=acreage, fill=type)) +
geom_bar(stat="identity", #position=position_dodge(),
         color = "black")+
  
  scale_fill_brewer(palette = "PRGn")+
  # scale_fill_manual(values=c(#"#000000",
  #   "#999999","#FFDB6D", 
  #                            "#C4961A" 
  # #"#F4EDCA", 
  #               #"#D16103", "#C3D7A4", "#52854C", "#4E84C4", "#293352"
  #               ))+
  scale_y_continuous(name = "Acres", labels = scales::comma) +
  xlab("Change From Previous Year")+
  theme_minimal() +
   theme(legend.position = c(0.4, 0.8))+
  theme(axis.text=element_text(size=12))+
  theme(legend.background = element_rect(size=0.5, linetype="solid"))+
  theme(legend.title = element_blank())+
  ggtitle("Change from Almond or Walnut")

```

ALMOND FAILURES MAP 
```{r}
per_fail <- diff_field_join %>% 
  as_tibble() %>% 
  pivot_longer(c(-OBJECTID_1, -acres, -geometry),
                                values_to="type", names_to="year") %>% 
  filter(type %in% c("almond -> rice", "walnut -> rice",
                     "almond -> annual crop", "walnut -> annual crop",
                     #"almond -> alfalfa", "walnut -> alfalfa", 
                     "almond -> fallow", "walnut -> fallow"
                     #"almond -> grasses", "walnut -> grasses"
                     )) %>%
  #filter(str_detect(type, pattern = c("almond ->", "walnut ->"))) %>% 
  #filter(str_detect(type, pattern = c("rice", "alfalfa", "annual crop", "fallow")))%>% 
  #filter(!type %in% c("almond -> almond" , "walnut -> almond",
   #                   "almond -> other other", "walnut ->)) %>% 
  rename("field size (acres)" = acres) %>% 
  st_sf() %>% 
  st_centroid()

tmap_mode("plot")
per_fail_map <- tm_basemap("OpenStreetMap.Mapnik") +
  tm_shape(per_fail) +
  tm_dots(col = "type", size = 0.5, alpha = 1, palette = "PRGn")+#, col = "year")+#, size = "field size (acres)")+
  tm_shape(counties)+
  tm_polygons(alpha = 0)+
  tm_text("NAME", size = 0.7, alpha = 0.5)+
   tm_layout(legend.outside = TRUE, legend.text.size = 1, title = "Change from Perennials", title.size = 2)
per_fail_map
getwd()
tmap_save(per_fail_map, filename="per_fail_map.png")
```


TO OTHER PERENNIAL (FROM ALL) PLOT - just to see how things look
```{r}
s <- diff_long %>%
  complete(year,type, fill = list(acres=2)) %>% 
  #filter(type %in% c("rice -> almond", "rice -> walnut", "rice -> other perennial")) %>% 
  filter(str_detect(type, pattern = "-> other perennial")) %>% 
  # filter(!type %in% c("almond -> walnut" ,
  #                     "walnut -> walnut",
  #                     "other other -> walnut"
  #                     )) %>% 
  group_by(year, type) %>%
  summarise(acreage = sum(acres)) %>% 
  ungroup() %>% 
  #group_by(year) %>% 
  mutate(type = fct_reorder(type, desc(acreage))) %>% 
  ungroup()
 
ggplot(data=s, aes(x=year, y=acreage, fill=type)) +
geom_bar(stat="identity", position=position_dodge(), color = "black")+
  scale_fill_manual(values=c("#000000","#999999","#FFDB6D", 
                             "#C4961A", "#F4EDCA", 
                "#D16103", "#C3D7A4", "#52854C", "#4E84C4", "#293352"))+
  scale_y_continuous(name = "Acres", labels = scales::comma) +
  xlab("Change From Previous Year")+
  theme_minimal() +
   theme(legend.position = c(0.3, 0.7))+
  theme(axis.text=element_text(size=12))+
  theme(legend.background = element_rect(size=0.5, linetype="solid"))+
  theme(legend.title = element_blank())+
  ggtitle("Change to OP")
 

```
ANNUAL DIFF PLOT
```{r}
s <- diff_long %>%
  complete(year,type, fill = list(acres=2)) %>% 
  filter(type %in% c("rice -> annual crop", "rice -> alfalfa", "rice -> other annual", "rice -> grasses")) %>% #, "rice -> other other")) %>% 
  group_by(year, type) %>%
  summarise(acreage = sum(acres)) %>% 
  mutate(type = fct_relevel(type, "rice -> annual crop", "rice -> alfalfa", "rice -> other annual", "rice -> grasses"))#, "rice -> other other"))
 
ggplot(data=s, aes(x=year, y=acreage, fill=type)) +
geom_bar(stat="identity", position=position_dodge(), color = "black")+
  scale_fill_manual(values=c("#999999", "#C4961A", "#56B4E9","#52854C"))+#, "#56B4E9","#293352"))+
  scale_y_continuous(name = "Acres", labels = scales::comma) +
  xlab("Change From Previous Year")+
  theme_minimal() +
   theme(legend.position = c(0.8, 0.8))+
  theme(axis.text=element_text(size=12))+
  theme(legend.background = element_rect(size=0.5, linetype="solid"))+
  theme(legend.title = element_blank())+
  ggtitle("From Rice to Annual Crop Changes")
 

```
ANNUAL TO RICE DIFF PLOT
```{r}
s <- diff_long %>%
  complete(year,type, fill = list(acres=2)) %>% 
  filter(type %in% c("annual crop -> rice", "alfalfa -> rice", "other annual -> rice","grasses -> rice")) %>%#, "other other -> rice")) %>% 
  group_by(year, type) %>%
  summarise(acreage = sum(acres)) %>% 
  mutate(type = fct_relevel(type, "annual crop -> rice", "alfalfa -> rice", "other annual -> rice","grasses -> rice"))#, "other other -> rice"))
 
ggplot(data=s, aes(x=year, y=acreage, fill=type)) +
geom_bar(stat="identity", position=position_dodge(), color = "black")+
  scale_fill_manual(values=c("#999999", "#C4961A", "#56B4E9","#52854C"))+#, "#56B4E9"))+#,"#293352"))+
  scale_y_continuous(name = "Acres", labels = scales::comma) +
  xlab("Change From Previous Year")+
  theme_minimal() +
   theme(legend.position = c(0.8, 0.8))+
  theme(axis.text=element_text(size=12))+
  theme(legend.background = element_rect(size=0.5, linetype="solid"))+
  theme(legend.title = element_blank())+
  ggtitle("From Anual Crop to Rice Changes")
 

```
#ANNUAL AND RICE INTERCHANGE PLOT
```{r}
an_r <- diff_long %>%
  complete(year,type, fill = list(acres=2)) %>% 
  filter(type %in% c("annual crop -> rice", "alfalfa -> rice", "other annual -> rice","grasses -> rice", "rice -> annual crop", "rice -> alfalfa", "rice -> other annual", "rice -> grasses")) %>%#, "other other -> rice")) %>% 
  mutate(what = case_when(str_detect(type, pattern = "-> rice") ~ "_ to rice",
                          str_detect(type, pattern = "rice ->") ~ "rice to _ ")) %>% 
  mutate(what = case_when(str_detect(type, pattern = "-> rice") ~ "to rice",
                          str_detect(type, pattern = "rice ->") ~ "from rice")) %>% 
  group_by(year, type, what) %>%
  summarise(acreage = sum(acres)) %>% 
  ungroup() %>% 
  mutate(hectares = acreage*0.404686) %>% 
  mutate(year = paste0("'",str_sub(year, start=3))) %>% 
  mutate(year = as_factor(year)) %>% 
  mutate(type = fct_reorder(type, desc(-acreage)))
 


### PLOT ###
an_r_plot <- ggplot(data=an_r, aes(x=year, y=hectares, fill=type)) +
geom_bar(stat="identity", color = NA)+
  # scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7"))+
  scale_fill_brewer(palette = "Set2")+
  scale_y_continuous(name = "ha", labels = scales::comma) +
  xlab("Change From Previous Year")+
  theme_bw() +
   theme(legend.position = "bottom")+
  theme(axis.text=element_text(size=12))+
  theme(legend.background = element_rect(size=0.5, linetype="solid"))+
  theme(legend.title = element_blank(),
        strip.background = element_blank(),
        #panel.grid.major = element_blank(), 
        #panel.grid.minor = element_blank(),
        legend.key.size = unit(1, 'cm'),
        legend.text = element_text(size = 10),
        strip.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 12),
        panel.grid.major.x = element_blank() ,
        )+
  coord_cartesian(ylim = c(1000,15000))+
  #ggtitle("Annuals to/from Rice ")+
  facet_wrap(what~.)
an_r_plot 
getwd()


ggsave(plot = an_r_plot, filename = "/Users/lukesalvato/Dropbox/Mac (3)/Documents/Land_Use/rice_rotation/ms/output/figures/annuals_and_rice_time_series_20220923.png", width = 9, height = 6)


ggsave(plot = an_r_plot, filename = "/Users/lukesalvato/Dropbox/Mac (3)/Documents/Land_Use/rice_rotation/ms/output/figures/annuals_and_rice_time_series_20220923.svg", width = 9, height = 6)



```


```{r}
from_rice_df <-an_r %>% filter(what == "from rice") %>% 
mutate(type = fct_reorder(type, desc(-acreage)))
  
from_rice_plot <- ggplot(data=from_rice_df, aes(x=year, y=hectares, fill=type)) +
geom_bar(stat="identity", color = NA)+
    scale_fill_manual(values=c( "#009E73", "#56B4E9", "#E69F00","#999999"
          #"#F0E442", "#0072B2", "#D55E00", "#CC79A7")
                             
                               ))+
  # scale_y_continuous(name = "ha", labels = scales::comma) +
  #scale_fill_brewer(palette = "PRGn")+
  xlab("Change From Previous Year")+
  theme_bw() +
   theme(legend.position = "bottom")+
  theme(axis.text=element_text(size=12))+
  theme(legend.background = element_rect(size=0.5, linetype="solid"))+
  theme(legend.title = element_blank(),
        strip.background = element_blank(),
        )
  #ggtitle("Annuals to/from Rice ")+
  #facet_wrap(what~.)
from_rice_plot
getwd()


to_rice_df <-an_r %>% filter(what == "to rice")%>% 
mutate(type = fct_reorder(type, desc(-acreage)))
  
to_rice_plot <- ggplot(data=to_rice_df, aes(x=year, y=hectares, fill=type)) +
geom_bar(stat="identity", color = NA)+
 # scale_fill_manual(values=c(
 #   
 #   
 #                             #"#FFDB6D",
 #                              #"#C4961A",
 #                              #"#F4EDCA",
 #                              #"#D16103" ,
 #                              "#C3D7A4",
 #                              "#52854C" ,
 #                              "#4E84C4",
 #                              "#293352"
 #                              ))+
 #  #scale_color_viridis()+
  scale_fill_brewer(palette = "PRGn", direction = -1, type = "seq")+
  xlab("Change From Previous Year")+
  theme_bw() +
   theme(legend.position = "bottom")+
  theme(axis.text=element_text(size=12))+
  theme(legend.background = element_rect(size=0.5, linetype="solid"),
        axis.text.y = element_blank())+
  theme(legend.title = element_blank(),
        strip.background = element_blank(),
        )+
  coord_cartesian(ylim = c(0,15000))+
labs(y = NULL)
  #ggtitle("Annuals to/from Rice ")+
  #facet_wrap(what~.)
to_rice_plot


both <- ggarrange(from_rice_plot, to_rice_plot)
both



ggsave(plot = an_r_plot, filename = "/Users/lukesalvato/Dropbox/Mac (3)/Documents/Land_Use/rice_rotation/ms/output/figures/annuals_and_rice_time_series_20220921.png", width = 9, height = 10)
```


ANNUALS TO FROM RICE MAP
```{r}
ann <- diff_field_join %>% 
  as_tibble() %>% 
  pivot_longer(c(-OBJECTID_1, -acres, -geometry),
                                 values_to="type", names_to="year") %>% 
  filter(type %in% c("annual crop -> rice", "alfalfa -> rice", "other annual -> rice","grasses -> rice", "rice -> annual crop", "rice -> alfalfa", "rice -> other annual", "rice -> grasses")) %>%
   mutate(change = case_when(str_detect(type, pattern = "-> rice") ~ " to rice",
                          str_detect(type, pattern = "rice ->") ~ "from rice")) %>%
  rename("field size (acres)" = acres) %>% 
  ungroup() %>% 
  st_sf() %>% 
  st_centroid()

tmap_mode("plot")
annual <- tm_shape(ann) +
  tm_dots(col = "change", size = 0.1, alpha = 0.9, palette = "Pastel1", legend.hist = TRUE)+#, col = "year", size = "field size (acres)")+
 # tm_shape(counties)+
  #tm_polygons(alpha = 0)+
  #tm_text("NAME", size = 0.7, alpha = 0.5)+
   tm_layout(legend.outside = TRUE, legend.text.size = 0.9 , title = "All annual types to/from rice",legend.title.size = 1.2)
annual
getwd()
#tmap_save(annual, filename="annual_to_rice_map.png")

```


FALLOW PLOT
```{r}

s <- diff_long %>%
  complete(year,type, fill = list(acres=2)) %>% 
  filter(type %in% c("fallow -> rice", "rice -> fallow")) %>% 
  group_by(year, type) %>%
  summarise(acreage = sum(acres)) %>% 
  mutate(type = fct_relevel(type, "fallow -> rice", "rice -> fallow"))
 
ggplot(data=s, aes(x=year, y=acreage, fill=type)) +
geom_bar(stat="identity", color = "black")+
  scale_fill_manual(values=c("#52854C","#C4961A"))+
  scale_y_continuous(name = "Acres", labels = scales::comma) +
  xlab("Change From Previous Year")+
  theme_minimal() +
   theme(legend.position = c(0.2, 0.8))+
  theme(axis.text=element_text(size=12))+
  theme(legend.background = element_rect(size=0.5, linetype="solid"))+
  theme(legend.title = element_blank())+
  ggtitle("Rice to/from Fallow")
  
  
 

```

FALLOW MAPS
```{r}
r_to_f <- diff_field_join %>% 
  as_tibble() %>% 
  pivot_longer(c(-OBJECTID_1, -acres, -geometry),
                                 values_to="type", names_to="year") %>% 
  filter(type %in% c("rice -> fallow")) %>%
  rename("field size (acres)" = acres) %>% 
  st_sf() %>% 
  st_centroid()

tmap_mode("plot")
r_to_f <- tm_shape(r_to_f) +
  tm_dots(col = "year", size = 0.1, alpha = 0.9, palette = "Paired")+#, col = "year", size = "field size (acres)")+
  tm_shape(counties)+
  tm_polygons(alpha = 0)+
  tm_text("NAME", size = 0.7, alpha = 0.5)+
   tm_layout(legend.outside = TRUE, legend.text.size = 1.5 , title = "Rice to Fallow")
r_to_f
getwd()
tmap_save(r_to_f, filename="rice_to_fallow_map.png")

f_to_r <- diff_field_join %>% 
  as_tibble() %>% 
  pivot_longer(c(-OBJECTID_1, -acres, -geometry),
                                 values_to="type", names_to="year") %>% 
  filter(type %in% c("fallow -> rice")) %>%
  rename("field size (acres)" = acres) %>% 
  st_sf() %>% 
  st_centroid()

library(RColorBrewer)

tmap_mode("plot")
f_to_r <- tm_shape(f_to_r) +
  tm_dots(col = "year", size = 0.1, alpha = 0.9, palette = "Paired")+ #, col = "year", size = "field size (acres)")+ palette = vir
  tm_shape(counties)+
  tm_polygons(alpha = 0)+
  tm_text("NAME", size = 0.7, alpha = 0.5)+
   tm_layout(legend.outside = TRUE, legend.text.size = 1.5 , title = "Fallow to Rice")
f_to_r
getwd()
tmap_save(f_to_r, filename="fallow_to_rice_map.png")


```

FALLOW MAPS SHOWING ONLY MAJOR YEARS
```{r}
r_to_f <- diff_field_join %>% 
  as_tibble() %>% 
  pivot_longer(c(-OBJECTID_1, -acres, -geometry),
                                 values_to="type", names_to="year") %>% 
  filter(year %in% c(2014, 2017)) %>% 
  filter(type %in% c("rice -> fallow")) %>%
  rename("field size (acres)" = acres) %>% 
  st_sf() %>% 
  st_centroid()


tmap_mode("plot")
r_to_f <- tm_shape(r_to_f) +
  tm_dots(col = "year", size = 0.1, alpha = 0.9, palette = "Dark2")+#, col = "year", size = "field size (acres)")+
  tm_shape(counties)+
  tm_polygons(alpha = 0)+
  tm_text("NAME", size = 0.7, alpha = 0.5)+
   tm_layout(legend.outside = TRUE, legend.text.size = 1.5 , title = "Rice to Fallow")
r_to_f
getwd()
tmap_save(r_to_f, filename="rice_to_fallow_map_2014_and_2017.png")



f_to_r <- diff_field_join %>% 
  as_tibble() %>% 
  pivot_longer(c(-OBJECTID_1, -acres, -geometry),
                                 values_to="type", names_to="year") %>% 
  filter(year %in% c(2016, 2018)) %>% 
  filter(type %in% c("fallow -> rice")) %>%
  rename("field size (acres)" = acres) %>% 
  st_sf() %>% 
  st_centroid()

#library(RColorBrewer)

tmap_mode("plot")
f_to_r <- tm_shape(f_to_r) +
  tm_dots(col = "year", size = 0.1, alpha = 0.9, palette = "Set1")+
#, col = "year", size = "field size (acres)")+ palette = vir
  tm_shape(counties)+
  tm_polygons(alpha = 0)+
  tm_text("NAME", size = 0.7, alpha = 0.5)+
   tm_layout(legend.outside = TRUE, legend.text.size = 1.5 , title = "Fallow to Rice")
f_to_r
getwd()
tmap_save(f_to_r, filename="fallow_to_rice_map_2016_and_2017.png")

```



SUMMARY PLOTS
```{r}
crops1 <- crops %>% 
  mutate(year = as_factor(year)) %>% 
  group_by(Crop) %>% 
  mutate(Crop = fct_reorder(Crop, desc(acres))) %>% 
  ungroup() %>% 
  mutate(year = paste0("'",str_sub(year, start=3))) 
  
unique(crops1$Crop) 
length(categories)

crops1 %>% 
  mutate(Crop = factor(Crop, levels = c("walnut", "almond","alfalfa", "other annual", "grasses", "other perennial", "other other", "annual crop","fallow","rice"))) %>% 
ggplot(aes(x=year, y=acres, fill=Crop, group = Crop)) +
geom_bar(stat="identity")+#, color = "black")+
  scale_fill_manual(values=c("#000000","#999999","#FFDB6D", "#C4961A", "#F4EDCA", 
                "#D16103", "#C3D7A4", "#52854C", "#4E84C4", "#293352"))+
  scale_y_continuous(name = "Acres", labels = scales::comma) +
  xlab("Crop totals by year")+
  theme_minimal() +
   #theme(legend.position = c(1.2, 1.2))+
  theme(axis.text=element_text(size=12))+
  theme(legend.background = element_rect(size=0.5, linetype="solid"))+
  theme(legend.title = element_blank())+
  ggtitle("Overall acreage")+ 
  geom_hline(yintercept=c(100000,200000,300000,400000,500000,600000), size = .5)


```


# RICE time series PLOT
```{r}
data_select %>% filter(CDL_class ==3) %>% 
  group_by(year) %>% 
  dplyr::summarise(acres=sum(acres))%>% 
  ggplot(aes(year, acres))+
  geom_line()+
  #labs(fill="Year") +
  scale_y_continuous(name = "Acres", labels = scales::comma) +
  geom_text(aes(x = year, y = acres, label = scales::comma(acres)), position = position_dodge(width = 1), vjust = -0.5, size = 3, labels = scales::comma)
```

	
